%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Josh Woodward} % Your name
\address{github.com/jdw6359}
\address{(413)-335-0258} % phone number
\address{josh.woodward2693@gmail.com} % email address

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Rochester Institute of Technology} \hfill {\em Rochester, NY} \\ 
B.S., Software Engineering \hfill Expected May 2016
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Relevant Skills and Tools}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages: & Ruby, Java, Python, C, C \#, VBScript\\
Application Frameworks: & Ruby on Rails, AngularJS, .NET (Entity Framework), \\
& Android SDK, Django, Classic ASP.NET\\
Front End Technologies: & HTML, CSS, Javascript, JQuery, SASS, Bootstrap\\
Datastores / Reporting: & SQL Server 2008 / 2012, SSRS, MySQL, PostgreSQL, \\
& Cassandra, Redis
\end{tabular}

\end{rSection}



%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Experience}

\begin{rSubsection}{Datto (Formerly Backupify)}{Boston, MA}{Software Engineering Intern}{May - August 2015}
\item Maintained Google Apps and Salesforce backup products following a Scrum development process.
\item Contributed Ruby scripts to Platform team to assist data migration from AWS to Datto Cloud. 
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Medisked, LLC}{Rochester, NY}{Software Engineering Contractor}{May 2014 - May 2015}
\item Designed, developed, and deployed quarterly enhancements to company's core product.
\item Led the development of e-MAR solution, as well as its integration into core platform.

{\sl Software Engineering Intern}\hfill{\sl May 2013 - January 2014}
\item Implemented a new web interface for the company's core product, according to proposed UI mockups.
\item Consulted and shadowed I/DD health care professionals, eliciting the functional 	requirements of industry-compliant eMAR product.   
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Rediker Software}{Hampden, MA}
{Software Development Intern}{May - August 2012}
\item Constructed Teacher Evaluator platform; reaching beta release after 10 weeks of development.
\item Conducted requirements gathering and application usability sessions with K-12 teachers and principals.
\item Served as subject matter expert over customizable dashboard analytics feature.
\end{rSubsection}

\end{rSection}



\begin{rSection}{Projects}
\begin{rSubsection}{Wegmans Scholarship Application (Senior Project)}{}{}{}
\item Established and followed scrum process, serving as product manager for team.
\item Application created using .NET with Entity Framework, SQL Server 2012, and Angular JS.
\end{rSubsection}

\begin{rSubsection}{Student Advising Application, RIT SE Department}{}{}{}
\item Enhanced advisor workflow through creation of web application used to manage student records. 
\item Held weekly meetings with advisors to discuss new feature requests and demo current progress.
\end{rSubsection}
\end{rSection}
%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
